ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-21 pyked.tex
Add idea for usage example
Remove acknowledgements
Update chemked spec

In addition to the meta information, the data encoded in the \ck{} file is in
a mapping called \yaml|datapoints|. The \yaml|datapoints| mapping contains a
sequence of nested mappings, with the following information for each element of
the sequence:
%
\begin{itemize}
    \item \yaml|temperature| (required, sequence): The temperature of the
    experiment, with units
    \item \yaml|ignition-delay| (optional, sequence): The ignition delay of the
    experiment, with units, if the \yaml|experiment-type| is \yaml|ignition
    delay|
    \item \yaml|flame-speed| (optional, sequence): The flame speed of the
    experiment, with units, if the \yaml|experiment-type| is \yaml|flame speed|
    \item \yaml|pressure| (required, string): The pressure of the experiment,
    with units
    \item \yaml|composition| (required, sequence): The composition of the
    mixture in the experiment, a sequence of mappings with the following fields
    \begin{itemize}
        \item \yaml|species-name| (required, string): The name of the species
        \item \yaml|mole-fraction|, \yaml|mass-fraction|, \yaml|mole-percent|
        (required, float): The mole fraction or percent, or the mass fraction.
        Only one of the three is permitted in a given \yaml|composition|
        sequence.
    \end{itemize}
    \item \yaml|ignition-type| (required, mapping); The type of ignition
    measured in the experiments. The required fields are
    \begin{itemize}
        \item \yaml|type| (required, string): How the ignition delay was
        measured, one of \yaml|d/dt max| to indicate the ignition point is
        found at the maximum of the time derivative of the \yaml|target|, or
        \yaml|max| or \yaml|min| to indicate the ignition point is at the
        maximum or minimum of the \yaml|target|
        \item \yaml|target| (required, string): The target for the type of the
        ignition point, one of \yaml|temperature|, \yaml|pressure|, \yaml|OH|,
        \yaml|OH*|, \yaml|CH|, or \yaml|CH*|
    \end{itemize}
\end{itemize}

@@

%====================================================================
\section{Use example}
%
\todo[inline]{Bryan/Kyle to do}

@@

%====================================================================
\section{Acknowledgements}
This research was funded by \ldots
\todo[inline]{update}
% Kyle: I don't think I have any funding yet to acknowledge for this

>>>>

In addition to the meta information, the data encoded in the \ck{} file is in
a mapping called \yaml|datapoints|. The \yaml|datapoints| mapping contains a
sequence of nested mappings, with the following information for each element of
the sequence:
%
\begin{itemize}
    \item \yaml|temperature| (required, sequence): The temperature of the
    experiment, with units
    \item \yaml|ignition-delay| (optional, sequence): The ignition delay of the
    experiment, with units, if the \yaml|experiment-type| is \yaml|ignition
    delay|
    \item \yaml|flame-speed| (optional, sequence): The flame speed of the
    experiment, with units, if the \yaml|experiment-type| is \yaml|flame speed|
    \item \yaml|pressure| (required, string): The pressure of the experiment,
    with units
    \item \yaml|composition| (required, sequence): The composition of the
    mixture in the experiment, a sequence of mappings with the following fields
    \begin{itemize}
        \item \yaml|species-name| (required, string): The name of the species
        \item \yaml|mole-fraction|, \yaml|mass-fraction|, \yaml|mole-percent|
        (required, float): The mole fraction or percent, or the mass fraction.
        Only one of the three is permitted in a given \yaml|composition|
        sequence.
        \item \yaml|InChI|, \yaml|SMILES|, \yaml|atomic-composition|, or
        \yaml|elemental-composition| (required, string or sequence): The InChI
        or SMILES representing the molecule, or its atomic or elemental
        composition (\yaml|atomic-composition| and \yaml|elemental-composition|
        are synonyms) as a sequence
    \end{itemize}
    \item \yaml|ignition-type| (required, mapping); The type of ignition
    measured in the experiments. The required fields are
    \begin{itemize}
        \item \yaml|type| (required, string): How the ignition delay was
        measured, one of \yaml|d/dt max| to indicate the ignition point is
        found at the maximum of the time derivative of the \yaml|target|, or
        \yaml|max| or \yaml|min| to indicate the ignition point is at the
        maximum or minimum of the \yaml|target|
        \item \yaml|target| (required, string): The target for the type of the
        ignition point, one of \yaml|temperature|, \yaml|pressure|, \yaml|OH|,
        \yaml|OH*|, \yaml|CH|, or \yaml|CH*|
    \end{itemize}
\end{itemize}

Each of the quantities in a datapoint must be specified with units. This should
be done as a single string associated with the first element of the sequence.
The units of the quantity are validated to ensure they have the appropriate
dimensionality for the quanity. In addition, each of the quantities in the
\yaml|datapoint| can optionally be assigned an uncertainty. This uncertainty can
be either absolute or relative, and is specified as elements of the sequence of
the associated key. For example, the absolute uncertainty of the temperature and
the relative uncertainty of the ignition delay might be specified as follows:

\begin{minted}{yaml}
datapoints:
  - temperature:
      - 1100 kelvin
      - uncertainty-type: absolute
        uncertainty: 10 kelvin
    ignition-delay:
      - 10 us
      - uncertainty-type: relative
        uncertainty: 10
    ...
\end{minted}

@@

%====================================================================
\section{Use example}
%
\todo[inline]{Bryan/Kyle to do}
\todo[inline]{Idea: CONV simulations using Cantera in a loop with conditions
from the Pandas output for butanol?}

@@
